### 2021-09-07 README.Rmd
added readme skeleton

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trolleyMultilabReplication

<!-- badges: start -->
<!-- badges: end -->

The goal of trolleyMultilabReplication is to provide

## Installation

The package is currently not on CRAN, but the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marton-balazs-kovacs/trolleyMultilabReplication")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(trolleyMultilabReplication)
## basic example code
```

### 2021-09-07 dev/dev.R

@@ -1,7 +1,6 @@
 # Add packages
 usethis::use_package("dplyr")
 usethis::use_package("kableExtra")
-usethis::use_package("papaja")
 usethis::use_package("lmerTest")
 usethis::use_package("jsonlite")
 usethis::use_package("vroom")

### 2021-12-15 R/create_plot_study1.R
- Merge plot1-2, and 3-4 - Tag panels - Add n

@@ -14,7 +14,7 @@ create_plot_study1 <- function(data) {
       x = condition,
       y = rate,
       fill = condition,
-      colour=condition) +
+      colour = condition) +
     geom_flat_violin(
       ggplot2::aes(
         y = rate,
@@ -25,7 +25,7 @@ create_plot_study1 <- function(data) {
       ggplot2::aes(
         y = rate,
         colour = condition),
-      position = ggplot2::position_jitter(width = .15),
+      position = ggplot2::position_jitter(width = .15, height = .25),
       size = .25,
       alpha= 0.8) +
     ggplot2::stat_summary(
@@ -44,7 +44,7 @@ create_plot_study1 <- function(data) {
     scale_colour_viridis_d() +
     ggplot2::facet_wrap(facets = vars(survey_name)) +
     ggplot2::labs(y = "To what extent is this action morally acceptable?") +
-    ggplot2::coord_cartesian(ylim = c(1, 9)) +
+    ggplot2::coord_cartesian(ylim = c(.5, 9.5), clip = "off") +
     ggplot2::scale_y_continuous(breaks = 1:9, expand = c(0, 0)) +
     ggplot2::theme_bw() +
     ggplot2::theme(
@@ -55,6 +55,7 @@ create_plot_study1 <- function(data) {
       axis.title.y = element_text(face = "bold", size = 10),
       axis.text.x = element_text(face = "bold", size = 7, colour = "Black"),
       axis.text.y = element_text(face = "bold", size = 12, colour = "Black"),
+      plot.margin = unit(c(5.5, 5.5, 11, 5.5), "pt"),
       legend.title = element_blank(),
       legend.text = element_text(size = 9),
       legend.position = "none")

### 2021-12-16 R/theme_trolley.R
Remove element_blanks() as that is easy to control in the plot

@@ -4,10 +4,9 @@ theme_trolley <- function() {
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     plot.title = element_text(hjust = 0.5, vjust = 0.5, face = "bold", size = 17),
-    axis.title.x = element_blank(),
+    axis.title.x = element_text(face = "bold", size = 10),
     axis.title.y = element_text(face = "bold", size = 10),
     axis.text.x = element_text(face = "bold", size = 10, colour = "Black"),
     axis.text.y = element_text(face = "bold", size = 12, colour = "Black"),
-    legend.title = element_blank(),
     legend.text = element_text(size = 9))
   }

### 2021-12-16 R/create_plot_country.R
Change theme, scales, and axes

@@ -17,25 +17,20 @@ create_plot_country <- function(data) {
       ggplot2::aes(
         size = N,
         color = Region)) +
-    ggplot2::guides(size = FALSE) +
+    ggplot2::guides(size = "none") +
     ggplot2::geom_text(hjust = -0.2, size = 3) +
     ggplot2::geom_smooth(
       method = "lm",
       mapping = ggplot2::aes(weight = N),
       color = "blue",
+      alpha = .5,
       show.legend = FALSE,
       se = F) +
-    ggplot2::xlab("Effect size") +
-    ggplot2::scale_y_continuous(breaks = c(0, 0.05, 0.1, 0.15), limits = c(0, 0.15)) +
-    ggplot2::scale_x_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8) )+
-    ggplot2::theme_bw() +
-    ggplot2::theme(
-      panel.grid.major = element_blank(),
-      panel.grid.minor = element_blank(),
-      plot.title = element_text(hjust = 0.5, vjust = 0.5, face = "bold", size = 17),
-      axis.title.y = element_text(face = "bold", size = 10),
-      axis.text.x = element_text(face = "bold", size = 10, colour = "Black"),
-      axis.text.y = element_text(face = "bold", size = 12, colour = "Black"),
-      legend.title = element_blank(),
-      legend.text = element_text(size = 9))
+    ggplot2::labs(x = "Cohen's d", y = NULL, color = NULL) +
+    ggplot2::scale_y_continuous(breaks = c(0, 0.05, 0.1, 0.15),
+                                limits = c(0, 0.15)) +
+    ggplot2::scale_x_continuous(breaks = seq(0, .9, .1),
+                                limits = c(0, .9))+
+
+    theme_trolley()
 }

### 2021-12-16 R/create_plot_ind_col.R
Flip, change scales

@@ -10,8 +10,8 @@ create_plot_ind_col <- function(data) {
   data %>%
     ggplot2::ggplot() +
     ggplot2::aes(
-      x = variable,
-      y = b,
+      y = variable,
+      x = b,
       width = 0.7) +
     ggplot2::geom_bar(
       stat = "identity",
@@ -20,13 +20,15 @@ create_plot_ind_col <- function(data) {
       width = 1.2) +
     ggplot2::geom_errorbar(
       aes(
-        ymin = lower,
-        ymax = higher),
+        xmin = lower,
+        xmax = higher),
       position = position_dodge(width = 0.7),
       colour = "Black",
       width = 0.2) +
-    ggplot2::labs(y = "Beta effect size") +
-    ggplot2::geom_hline(yintercept = 0) +
-    ggplot2::scale_y_continuous(breaks = c(-0.15, -0.1, -0.05, 0, 0.05, 0.1, 0.15), limits=c(-0.15,0.15)) +
+    ggplot2::labs(x = "Std. Beta (SEM)",
+                  y = NULL) +
+    ggplot2::geom_vline(xintercept = 0) +
+    ggplot2::scale_x_continuous(breaks = seq(-.10, .10, .05),
+                                limits = c(-0.10,0.10)) +
     theme_trolley()
 }

### 2021-12-17 R/create_plot_country.R
Add axis title

@@ -26,7 +26,7 @@ create_plot_country <- function(data) {
       alpha = .5,
       show.legend = FALSE,
       se = F) +
-    ggplot2::labs(x = "Cohen's d", y = NULL, color = NULL) +
+    ggplot2::labs(x = "Eta squared", y = "Collectivism", color = NULL) +
     ggplot2::scale_y_continuous(breaks = c(0, 0.05, 0.1, 0.15),
                                 limits = c(0, 0.15)) +
     ggplot2::scale_x_continuous(breaks = seq(0, .9, .1),

### 2021-12-17 R/create_plot_study2.R

@@ -24,9 +24,10 @@ create_plot_study2 <- function(data) {
                      alpha = .8) +
     ggplot2::geom_point(aes(y = rate,
                             color = personal_force),
-                        position = position_jitter(width = .15),
+                        position = ggplot2::position_jitter(width = .15, height = .25),
                         size = .25,
-                        alpha= 0.8) +
+                        alpha = 0.8,
+                        show.legend = FALSE) +
     ggplot2::scale_fill_viridis_d() +
     ggplot2::scale_color_viridis_d() +
     ggnewscale::new_scale_color() +
@@ -36,11 +37,13 @@ create_plot_study2 <- function(data) {
                              position = position_nudge(x = .3, y = 0)) +
     ggplot2::scale_color_manual(values = c("white", "black")) +
     ggplot2::facet_wrap(~survey_name) +
-    ggplot2::labs(y = "To what extent is this action morally acceptable?") +
-    ggplot2::coord_cartesian(ylim = c(1, 9)) +
-    ggplot2::scale_y_continuous(breaks = 1:9, expand = c(0,0)) +
+    ggplot2::labs(y = "To what extent is this action morally acceptable?",
+                  x = NULL) +
+    ggplot2::coord_cartesian(ylim = c(.5, 9.5), clip = "off") +
+    ggplot2::scale_y_continuous(breaks = 1:9, expand = c(0, 0)) +
     theme_trolley() +
-    ggplot2::theme(legend.position = "bottom")
+    ggplot2::theme(legend.position = "bottom",
+                   legend.title = element_blank()) # This is needed bc of complicated new scales
 
 }
 

### 2021-12-17 R/theme_trolley.R

@@ -7,6 +7,6 @@ theme_trolley <- function() {
     axis.title.x = element_text(face = "bold", size = 10),
     axis.title.y = element_text(face = "bold", size = 10),
     axis.text.x = element_text(face = "bold", size = 10, colour = "Black"),
-    axis.text.y = element_text(face = "bold", size = 12, colour = "Black"),
+    axis.text.y = element_text(face = "bold", size = 10, colour = "Black"),
     legend.text = element_text(size = 9))
   }

### 2021-12-17 R/calculate_contact_stat.R
required changes by proof

@@ -10,14 +10,7 @@
 #' @return a tibble that contains the selected statistics
 #'   in a format that can be printed
 #' @export
-
-
-
-calculate_contact_stat <- function(data = NULL,
-                                     vars = NULL,
-                                     label = NULL,
-                                     rscale){
-
+calculate_contact_stat <- function(data = NULL, vars = NULL, label = NULL, rscale) {
   data %>%
     tibble::as_tibble() %>%
     dplyr::select(Region, {{vars}}) %>%
@@ -25,11 +18,12 @@ calculate_contact_stat <- function(data = NULL,
     tidyr::nest() %>%
     dplyr::arrange(Region) %>%
     dplyr::mutate(data_long = purrr::map(data,
-                                         ~tidyr::pivot_longer(.x,
-                                                              cols = everything(),
-                                                              names_to = "condition",
-                                                              values_to = "rate",
-                                                              values_drop_na = TRUE) %>%
+                                         . %>%
+                                           tidyr::pivot_longer(
+                                             cols = everything(),
+                                             names_to = "condition",
+                                             values_to = "rate",
+                                             values_drop_na = TRUE) %>%
                                            as.data.frame()),
                   bttest = purrr::map(data_long,
                                       ~BayesFactor::ttestBF(formula = rate ~ condition, data = .x,

### 2021-12-17 R/summarise_study.R

@@ -12,11 +12,12 @@ summarise_study <- function(data = NULL){
   stopifnot(!is.null(data))
 
   data %>%
-    dplyr::summarise(N = dplyr::n(),
-              `Age Mean` = mean(Age, na.rm = TRUE),
-              `Age SD` = sd(Age, na.rm = TRUE),
-              `Male %` = mean(Gender == 1, na.rm = TRUE),
-              `Higher education %` = mean(`Higher education`, na.rm = TRUE),
-              .groups = "drop")
+    dplyr::summarise(
+      N = dplyr::n(),
+      `Age Mean` = mean(Age, na.rm = TRUE),
+      `Age SD` = sd(Age, na.rm = TRUE),
+      `Male %` = mean(Gender == 1, na.rm = TRUE),
+      `Higher education %` = mean(`Higher education`, na.rm = TRUE),
+       .groups = "drop")
 
 }

### 2022-02-21 README.Rmd
updated documentation

@@
 
-The goal of trolleyMultilabReplication is to provide
+The goal of __trolleyMultilabReplication__ is to provide a structure for the data cleaning and analysis of the PSA006 trolley multilab replication project.
+You can find out more about the project at the projects' [OSF repository](https://osf.io/efy2w/).
 
@@
 ```
-## Example
 
-This is a basic example which shows you how to solve a common problem:
+## Description of the package
 
-```{r example}
-library(trolleyMultilabReplication)
-## basic example code
+The package includes high-level data cleaning and and data analyzing functions for the project.
+The functions are moderately documented.
+The documentation will be expanded in the future.
+To check the documentation of a given function use the following format `?trolleyMultilabReplication::calculate_study1_stat`.
+
+### Data
+
+The code for data cleaning can be found in the 'data-raw/' folder of the package.
+The data wrangling for the source data imported directly from Qualtrics can be found in the 'data-raw/trolley_raw.R' file.
+
+The raw datafile for the replication that contains the data from all of the data collection sites can be found in a .csv format in the 'extdata/' folder and called 'trolley_raw.csv'.
+
+You can load this datafile if you are replicating the results of the study by the following code:
+
+``` r
+trolley_raw <- system.file("extdata", "trolley_raw.csv", package = "trolleyMultilabReplication")
 ```
+
+The steps for preprocessing the raw datafile can be found in the 'raw-data/trolley_preprocessed.R' file.
+The code for creating the final processed datafile can be found in the 'data-raw/trolley.R' file.
+
+The codebook for the processed datafile can be found by running the following function: `?trolleyMultilabReplication::trolley`.
+This codebook contains the description of the most important variables for the raw data as well.
+
+The preprocessed data, the processed data, and the datafile containing the cultural distance scores for each country are saved as package data files and can be loaded by the following functions:
+
+``` r
+# List the datafiles saved as package data
+data(package = "trolleyMultilabReplication")
+# Cultural distance data
+trolleyMultilabReplication::cultural_distance
+# Preprocessed data
+trolleyMultilabReplication::trolley_preprocessed
+# Processed data
+trolleyMultilabReplication::trolley
+```
+
+### Analysis code
+
+The analysis code that we used for this project including the code for the creations of the tables and figures can be found in the 'vignettes' folder.
+The figures for the project in .pdf format can be found in the 'vignettes/figures/' folder.

### 2022-02-21 R/trolley.R

@@ -1,0 +1,109 @@
+#' Codebook for the processed datafile
+#'
+#' This datafile contains the codebook for the processed data of
+#' the PSA006 Trolley multilab replication.
+#'
+#' @format A dataframe with 27502 rows and 152 variables:
+#' \describe{
+#'   \item{survey_name}{character, Either "PSA006_Eastern", "PSA006_Southern", or "PSA006_Western". The distinction is only important because of the materials.}
+#'   \item{survey_id}{character, Unique id corresponding to the survey_name.}
+#'   \item{StartDate}{date, Datetime at the start of the completition of the survey.}
+#'   \item{EndDate}{date, Datetime at the end of the completition of the survey.}
+#'   \item{ResponseId}{character, Unique indetifier of the respondent.}
+#'   \item{trolley_1_resp}{integer, Response for the trolley footbridge pole dilemma. Either 1 for "yes" or 2 for no".}
+#'   \item{trolley_1_rate}{integer, Rating of moral acceptability for the trolley footbridge pole dilemma. Using 9 point Likert-type scale, 1 is "Completely unacceptable" while 9 is "Completely acceptable".}
+#'   \item{trolley_1_just}{character, Justification for the trolley footbridge pole dilemma.}
+#'   \item{trolley_2_resp}{integer, Response for the trolley footbridge switch dilemma. Either 1 for "yes" or 2 for "no".}
+#'   \item{trolley_2_rate}{integer, Rating of moral acceptability for the trolley footbridge switch dilemma. Using 9 point Likert-type scale, 1 is "Completely unacceptable" while 9 is "Completely acceptable".}
+#'   \item{trolley_2_just}{character, Justification for the trolley footbridge switch dilemma.}
+#'   \item{trolley_3_resp}{integer, Response for the trolley standard switch dilemma. Either 1 for "yes" or 2 for "no".}
+#'   \item{trolley_3_rate}{integer, Rating of moral acceptability for the trolley standard switch dilemma. Using 9 point Likert-type scale, 1 is "Completely unacceptable" while 9 is "Completely acceptable".}
+#'   \item{trolley_3_just}{character, Justification for the trolley standard switch dilemma.}
+#'   \item{trolley_4_resp}{integer, Response for the trolley standard footbridge dilemma. Either 1 for "yes" or 2 for "no".}
[…]
